Name matching through deep learning

### 2018-11-19 old/paper2018/introduction2.tex
words

We compared multiple proposed local loss functions---Schroff\cite{DBLP:conf/cvpr/SchroffKP15}, improved\cite{Zhang:2016:DML:3088616.3088665}, and angularcite{DBLP:journals/corr/abs-1708-01682}---and we found an adaptation of the triplet loss function proposed in \cite{DBLP:conf/cvpr/SchroffKP15} was better.

>>>>

We compared multiple proposed local loss functions---Schroff\cite{DBLP:conf/cvpr/SchroffKP15}, improved\cite{Zhang:2016:DML:3088616.3088665}, and angular\cite{DBLP:journals/corr/abs-1708-01682}---and we found an adaptation of the triplet loss function proposed in \cite{DBLP:conf/cvpr/SchroffKP15} was better.
